\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 5.0530 sec & 5.4318 sec & 0.0207 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}

>>>>

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}
